---
title: "FirstMarkdown"
output: 
  html_document:
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)
library(tidyverse)
library(kableExtra)
library(praise)
```

# About The Data

```{r about}

gm <- gapminder::gapminder
str(gm)
head(gm) %>%
  kable() %>%
  kable_styling()
```


### Questions:
- Which country has the highest GDP Per Capita? Lowest?
- Which country has the highest population? Lowest?

### How many unique countries are there? 
```{r num_countries}
length(unique(gm$country))
```
There are `r length(unique(gm$country))` unique countries

### How many countries are there per continent? 
```{r countriers_per_continent}
gm %>%
  group_by(continent) %>%
  summarise(num_countries=n_distinct(country))
```

### Which years are represented? 
``` {r year}
table(gm$year)
summary(gm$year)
```

### What is the average life expectancy in the entire dataset? 
```{r life_expectancy}
gm %>%
  summarise(avgLifeExp = mean(lifeExp))
```

### What is the average life expectancy across years? 
```{r life_across_years}
gm %>%
  group_by(year) %>%
  
  summarise(avgLifeExp = mean(lifeExp))
```
### Praise Break
```{r praise}
praise()
praise()
praise()
```

### Which countries had the lowest population in 1952?
```{r population}
gm %>%
  filter(year == 1952) %>%
  arrange(desc(pop)) %>%
  tail(10)
```

### What was the GDP Per Capita of Burundi in 2002? 
```{r gdpPerCap}
gm %>%
  filter(year== 2002 & country== "Burundi") %>%
  select(c(country, year, gdpPercap))
 
```

### Graph
``` {r graph}
ggplot(data = gm) +
  geom_boxplot(aes(x=year, y=lifeExp, group=year))
```


### Outlier in 1992...
```{r outlier}
gm %>%
  filter(year== 1992) %>%
  arrange(desc(lifeExp)) %>%
  tail(1)
```

