---
title: "538 Data"
author: "Dan Murphy"
date: "9/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(praise)
library(htmlwidgets)
```

```{r dataset_packages}
library(datasets)
library(dslabs)
library(openintro)
library(fivethirtyeight)

```

### Trying to load Daily Show dataset and display first few rows
```{r load_daily_show_data}
ds <- fivethirtyeight::daily_show_guests
str(ds)
head(ds)
```
Accessed the first six rows and successfully loaded the data (2693 Rows by 5 Columns )

### Looking at Guests who have appeared > 5 times
```{r num_appearances_desc}
ds %>%
  count(raw_guest_list) %>%
  arrange(desc(n)) %>%
  filter(n > 5)
  

```
Returned 38 rows and 2 columns, raw_guest_list and n. Fareed Zakaria appeared 19 times  14 people appeared 6 times.

### Load data from the "group" column and filter only Science
```{r group_data}
ds %>%
  count(group) %>%
  arrange(desc(group)) %>%
  filter(as.character(group)=="Science")
```
Returns group and n, Science and 28

### Load data from the group column and arrange the dates
```{r date_filtering}
ds %>%
  count(show) %>%
  arrange(desc(show))
```
Displaying Dates, begins in 1999

### Number of Shows Per Year
```{r shows_per_year}
ds %>%
  count(year)
```
Displaying the number of shows per year. Starts in 1999 with 166


### Alphabetize the raw_guest_list column to search for duplicate/ misspelled names
``` {r guest_list_names}
ds %>%
  count(raw_guest_list) %>%
  arrange(raw_guest_list)
```
Arrange the raw guest list , begins with (no guest) and (None) and the Aaron Brown, ... , Marci Hamilton

### Playing with Strings
```{r str}
string1 <- "This is a string"
str_length(string1)
```
Returns string length of string 1... 16

### Playing with Strings 2
```{r str2}
str_sort(c("banana", "apple", "honeydew"), locale="en")
```
Sort Strings => apple, banana, honeydew

### Playing With Strings 3
```{r str3}
str_view(c("apple", "banana", "anbanban"), ".an.")

```
Matching 'an' in strings with regex

### Playing with Strings 4
```{r str4}
div <- "a\\b"
writeLines(div)
str_view(div, "\\\\")
```
Using "\" to escape a backslash and regex to find "\" in a string



